---
title: "Keras MNIST tutorial"
output: html_notebook
---

```{r setup}
library(keras)
mnist <- dataset_mnist()
```

```{r}
X_train <- mnist$train$x
y_train <- mnist$train$y

X_test <- mnist$test$x
y_test <- mnist$test$y
```

```{r}
## Reshaping the dataset
X_train <- array_reshape(X_train, dim = c(nrow(X_train), 28*28))
X_test <- array_reshape(X_test, dim = c(nrow(X_test), 28*28))
```

The y data is an integer vector with values ranging from 0 to 9. To prepare this data for training we one-hot encode the vectors into binary class matrices using the Keras to_categorical() function:
```{r}
y_train <- to_categorical(y_train)
y_test <- to_categorical(y_test, 10)
```

DEFINING THE MODEL
The core data structure of Keras is a model, a way to organize layers. The simplest type of model is the Sequential model, a linear stack of layers.

We begin by creating a sequential model and then adding layers using the pipe (%>%) operator:

```{r}
model2 <- keras_model_sequential()

model2 %>%
  layer_dense(units = 256, input_shape = 784) %>%
  layer_activation("relu") %>%
  layer_dropout(rate = 0.4) %>%
  layer_dense(units = 128) %>%
  layer_activation("relu") %>%
  layer_dropout(rate = 0.3) %>%
  layer_dense(units = 10) %>%
  layer_activation("softmax")
  

model2
```

```{r}
model <- keras_model_sequential() 
model %>% 
  layer_dense(units = 256, activation = 'relu', input_shape = c(784)) %>% 
  layer_dropout(rate = 0.4) %>% 
  layer_dense(units = 128, activation = 'relu') %>%
  layer_dropout(rate = 0.3) %>%
  layer_dense(units = 10, activation = 'softmax')
```

```{r}
summary(model)
```

Next, compile the model with appropriate loss function, optimizer, and metrics:
```{r}
model %>%
  compile(optimizer = optimizer_rmsprop(lr = 0.001),
          loss = "categorical_crossentropy",
          metrics = "accuracy")
```


Use the fit() function to train the model for 30 epochs using batches of 128 images:
```{r}
history <- model %>%
  fit(X_train, y_train, epochs = 30, batch_size = 128, validation_split = 0.2)
```

```{r}
plot(history)
```


```{r}
model %>% evaluate(X_test, y_test)
```

```{r}
model %>% predict_classes(X_test[1:100, 1:784])
```

```{r}
mnist$test$y[1:100]
```






